---
title: "Motor Trend Analysis"
author: "Tianxiang(Ivan) Liu"
date: "16 September 2014"
output: html_document
---

### Executive Summary
The objective of this analysis is to compare the miles per garlon (MPG) performance of motors with different transmission type (automatic and mannual). In details, this report reveals which type of transmission is better to cars' MPG performance and how much differences between them. Meanwhile, other factors would also be considered during the analysis. The regression analysis will be implemented in this study to find the relationships between MPG and other various cars' factors.

---

### Exploratory Analysis

```{r message=FALSE, warning=FALSE, fig.width=6, fig.align='center', fig.height=3, echo=TRUE, error=FALSE}
data(mtcars)
names(mtcars) <- c('MPG','Cylinders','Displacement','Horsepower','RearRatio','Weight','MileTime','VS','Transmission','Gear','Carburetors')
mtcars[which(mtcars$Transmission==1),9] <- 'manual'
mtcars[which(mtcars$Transmission==0),9] <- 'automatic'
mtcars$Cylinders <- as.factor(mtcars$Cylinders)
mtcars$VS <- as.factor(mtcars$VS)
mtcars$Transmission <- as.factor(mtcars$Transmission)
mtcars$Gear <- as.factor(mtcars$Gear)
mtcars$Carburetors <- as.factor(mtcars$Carburetors)
par(mfcol = c(1,2))
boxplot(MPG~Transmission, data=mtcars, xlab='Transmission Type',ylab='Miles Per Gallon')
plot(density(mtcars$MPG),data=mtcars)
```

---

### Model Selection

```{r message=FALSE, warning=FALSE, fig.width=6, fig.align='center', fig.height=3, echo=TRUE, error=FALSE}

```

---

### Interpret Coefficient

```{r message=FALSE, warning=FALSE, fig.width=6, fig.align='center', fig.height=3, echo=TRUE, error=FALSE}

```

---

### Diagonosis (Residual)

```{r message=FALSE, warning=FALSE, fig.width=6, fig.align='center', fig.height=3, echo=TRUE, error=FALSE}

```

---

### Uncertanty Inference

```{r message=FALSE, warning=FALSE, fig.width=6, fig.align='center', fig.height=3, echo=TRUE, error=FALSE}
str(mtcars)
```

According to the above summary, we can see that the training datasets for this regression analysis are really small, which has only 32 observations. It means the further statistical inference based on the existing datasets are highly possible to be biased. Because the number of observations of each variable is to small to say they are normal distributed and linear related to dependent variable.

---

### Conclusion

```{r message=FALSE, warning=FALSE, fig.width=6, fig.align='center', fig.height=3, echo=TRUE, error=FALSE}

```

---