---
title: "Motor Trend Analysis"
author: "Tianxiang(Ivan) Liu"
date: "16 September 2014"
output: html_document
---

### Executive Summary
The objective of this analysis is to compare the miles per garlon (MPG) performance of motors with different transmission type (automatic and mannual). In details, this report reveals which type of transmission is better to cars' MPG performance and how much differences between them. Meanwhile, other factors would also be considered during the analysis. The regression analysis will be implemented in this study to find the relationships between MPG and other various cars' factors.

---

### Exploratory Analysis

```{r message=FALSE, warning=FALSE, fig.width=8, fig.align='center', fig.height=4, echo=TRUE, error=FALSE}
data(mtcars)
names(mtcars) <- c('MPG','Cylinders','Displacement','Horsepower','RearRatio','Weight','MileTime','VS','Transmission','Gear','Carburetors')
mtcars[which(mtcars$Transmission==1),9] <- 'manual'
mtcars[which(mtcars$Transmission==0),9] <- 'automatic'
mtcars$Cylinders <- as.factor(mtcars$Cylinders)
mtcars$VS <- as.factor(mtcars$VS)
mtcars$Transmission <- as.factor(mtcars$Transmission)
mtcars$Gear <- as.factor(mtcars$Gear)
mtcars$Carburetors <- as.factor(mtcars$Carburetors)
par(mfcol = c(1,2))
plot(density(mtcars$MPG)$x,density(mtcars$MPG)$y, xlab="MPG",ylab=NA)
boxplot(MPG~Transmission, data=mtcars, xlab='Transmission Type',ylab='Miles Per Gallon')
```

The first diagram above shows that the MPG of motors in train datasets follows normal distribution well which is good for regression analysis. The second diagram reveals a breif description regarding MPG by different transmission types. We can see from the plot that manual motors consume less fuels than automatic motors because both the mean and spred of MPG of manual cars are higher than that of cars with automatic transmission.

---

### Model Selection

The model uses both stepwise search to select the most important variables of model. All the factors are included in this model. Following is the details of the final model selected under stepwise method.

```{r message=FALSE, warning=FALSE, fig.width=6, fig.align='center', fig.height=3, echo=TRUE, error=FALSE}
fit1 <- lm(MPG~., data=mtcars)
fit2 <- step(fit1,direction='both', k=2, trace=0)
fit2$coef
```

We can see that a significant part of variables are removed and the remaining factors are important. We can also see that the transmission type has been selected in the model.

We also test the model with only transmission as independent variable and compare it with the previous two models. Following are the results of comparison.

```{r message=FALSE, warning=FALSE, fig.width=6, fig.align='center', fig.height=3, echo=TRUE, error=FALSE}
fit3 <- lm(MPG~Transmission, data=mtcars)
anova(fit3,fit2,fit1)
```

From the results above, from model 3 to model 2, it has a P-value of 1.476e-05 which means it is worthy to accept model 2 while the P-value of model three is much larger than 0.05, so there is not much diffences to add extra variables in model 3. Lastly, we select model 2 as our final model.

---

### Interpret Coefficient

Here we are going to interpret the coefficients of our final model. The details of the model have been displayed below.

```{r message=FALSE, warning=FALSE, fig.width=6, fig.align='center', fig.height=3, echo=TRUE, error=FALSE}
summary(fit2)
```

---

### Diagonosis (Residual)

```{r message=FALSE, warning=FALSE, fig.width=6, fig.align='center', fig.height=3, echo=TRUE, error=FALSE}

```

---

### Uncertanty Inference

```{r message=FALSE, warning=FALSE, fig.width=6, fig.align='center', fig.height=3, echo=TRUE, error=FALSE}
str(mtcars)
```

According to the above summary, we can see that the training datasets for this regression analysis are really small, which has only 32 observations. It means the further statistical inference based on the existing datasets are highly possible to be biased. Because the number of observations of each variable is to small to say they are normal distributed and linear related to dependent variable.

---

### Conclusion

```{r message=FALSE, warning=FALSE, fig.width=6, fig.align='center', fig.height=3, echo=TRUE, error=FALSE}

```

---